\begin{thebibliography}{9}
\bibitem{rel:silas}
Silas Boyd-Wickizer, Austin T. Clements, Yandong Mao, Aleksey Pesterev,
M. Frans Kaashoek, Robert Morris, and Nickolai Zeldovich
``An Analysis of Linux Scalability to Many Cores''
{\em In Proceedings of the 9th Symposium on Operating Systems Design and Implementation (OSDI 2010)}, Vancouver, Canada, October 2010.

\bibitem{rel:vm55}
``VMware Workstation 5.5 release note''
{\em Nov 06, 2008, http://www.vmware.com/support/ws55/doc/ws\_devices\_2way\_vsmp.html} 

\bibitem{rel:amd6core}
``AMD Opteron 6168 configuration''
{\em http://www.newegg.com/Product/Product.aspx?Item=N82E16819105267}

\bibitem{rel:splash2}
Steven Cameron Woo, Moriyoshi Ohara, Evan Torrie,Jaswinder Pal Singh,
and Anoop Gupt
``The SPLASH-2 Programs: Characterization and Methodological Considerations''
{\em In the Proceedings of the 22nd Annual International Symposium on Computer Architecture, June 1995}

\bibitem{rel:coremu}
Zhaoguo Wang, Ran Liu, Yufei Chen, Xi Wu, Haibo Chen, Weihua Zhang, Binyu Zang
``COREMU: a scalable and portable parallel full-system emulator.''
{\em PPOPP 2011: 213-222}

\bibitem{rel:qemuwiki}
``QEMU''
{\em Wikipedia, http://en.wikipedia.org/wiki/QEMU}

\bibitem{rel:steven}
Steven Cameron Woo, Moriyoshi Ohara, Evan Torrie, Jaswinder Pal Singh, and Anoop Gupta. 
``The SPLASH-2 programs: characterization and methodological considerations''
{\em SIGARCH Comput. Archit. News 23, 2 (May 1995), 24-36. DOI=10.1145/225830.223990 http://doi.acm.org/10.1145/225830.223990} 

\bibitem{rel:redisweb}
``REDIS'' {\em http://redis.io/}

\bibitem{rel:hiushan}
HiuShan Yim
{\em Evaluating the Performance Characteristics of a Virtual Machine Used on Simultaneous Multi-Threaded (SMT) Processors}
Master Thesis, Graduate School-New Brunswick Rutgers, 
The State University of New Jersey, 2000.

\bibitem{rel:xenpar}
Stephen Shankland
``Xen getting multiprocessor support''
{\em CNET News, http://news.cnet.com/Xen-getting-multiprocessor-support/2100-7344\_3-5741373.html}

\bibitem{rel:oceanscale}
Heinrich, Mark and Chaudhuri, Mainak
``Ocean warning: avoid drowning''
{\em SIGARCH Comput. Archit. News, Vol. 31, pp. 30-32}
\bibitem{rel:oceanscale2}
Michael Dipperstein
``SPLASH-2 Ocean Performance Analysis''
{\em http://michael.dipperstein.com/ocean/speedup.ps}

\bibitem{rel:xen}
Paul Barham, Boris Dragovic, Keir Fraser, Steven Hand, Tim Harris, Alex Ho, Rolf Neugebauer, Ian Pratt, and Andrew Warfield. 2003.
``Xen and the art of virtualization.''
{\em In Proceedings of the nineteenth ACM symposium on Operating systems principles (SOSP '03). ACM, New York, NY, USA, 164-177. DOI=10.1145/945445.945462 http://doi.acm.org/10.1145/945445.945462}

\end{thebibliography}

