\section{How I get it}

\paragraph{} At this moment of time, it would help much more to set up some realistic and specific targets.

\paragraph{Healthy and strong body.} Intense basketball games are no more appropriate for me to play in daily life. Instead, daily morning jogging, weekly swimming and body building will help in improving body conditions. Rather than muscles, I prefer a healthy body obtained by regular life, reasonable food and proper training. It's never late to start a training program.

\paragraph{Rich experiences and broad view.} It will be pretty good if I am able to have the experiences of attending and giving presentation on top technical conferences, visiting another research group, and spending an internship in one or two big companies. On the other hand, it is also important to explore another relative research area, and to construct some personal interesting projects.

\paragraph{Professional communication skills}, including languages, speaking skills and cultural knowledge. As Dawn asked me at Berkeley, it is the time to stop reading or watching any Chinese materials. Trying to write and speak in English is also important.
Let's take a look at the Chinese materials in my daily life:
\begin{itemize*}
\item \emph{SNS, Chinese emails and IM chatting. } Let me reduce the frequency of checking SNS to less than once per day. For Chinese emails, responses should be written in English whenever it is possible. So are responses in IM tools.
\item \emph{Online fictions and comics. } Easy. Stop reading any new online fictions or comics. It is better to explore some new hobbies.
\item \emph{New, especially NBA news. } Take Yahoo instead of Sina.com. Use Google Reader and Pulse for newsletter.
\item \emph{Films, as well as other videos. } For English films and TV series, display no subtitles. Start watching a series of American shows, such like \emph{Friends}.
\end{itemize*}

\subsection{To-do list}
\input{ToDoList.tex}

\subsection{File storage}

\begin{tabular}{|l|l|}
  \hline
  Item & Storage place \\
  \hline
  Office documents & Google Docs (dragonghy@gmail.com) \\
  PDF \emph{reading} materials & Dropbox (dragonghy@gmail.com) \\
  \LaTeX documents & Google Code (dragonghy@gmail.com) \\
  Photos & Picasa Web Albums (dragonghy@gmail.com) \\
  Source codes & Google Code (dragonghy@gmail.com) \\
  Programming competition & Google Code (dragonghy@gmail.com) \\
  Emails & Gmail (dragonghy@gmail.com) \\
  Contacts & Google Contact (dragonghy@gmail.com) \\
  Calendar & Google Calendar (dragonghy@gmail.com) \\
  Chinese SNS & Renren.com \\
  English SNS & Facebook \\
  Research Website & \emph{TBD} \\
  Personal Website & http://sites.google.com/site/thecoldor/ \\
  Private Website & http://coldor.wordpress.com/ \\
  Projects and large files & External drives \\
  Private and protected files & External drives \\
  Time-control reports & RescueTime.com (dragonghy@gmail.com) \\
  \hline
\end{tabular}
