\tolerance=10000

%============= document settings ==================
%
%\documentstyle[twocolumn,epsf,rotate,aps]{revtex}
%\documentstyle[epsf,rotate]{article}
%\documentstyle[prl,epsf,rotate,aps]{revtex}
\documentclass[12pt,epsf,a4paper,oneside,fleqn]{article}
%\usepackage{txfonts}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage[ruled, noresetcount]{algorithm2e}
\usepackage{graphicx,epsfig,latexsym,amsmath,amsthm,amssymb,color,fancybox,hyperref}

%============= page settings ======================

\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}

\pagestyle{headings} 
\linespread{1.3} 
\setlength{\textwidth}{17.0cm}
\setlength{\oddsidemargin}{-0.5cm}
\setlength{\evensidemargin}{-0.5cm}

\setlength{\textheight}{25.0cm} 
\setlength{\topmargin}{-1.1cm}
\setlength{\headheight}{0.85cm}

\setlength{\headsep}{0.4cm} 
\setlength{\jot}{0.4cm}

\title{Study Plan at Columbia University in New York}
\author{Huayang Guo
}

\begin{document}
\date{\today}
\maketitle
\par

\section{Foreword}

\begin{comment}
十年寒窗，PhD将会是步入社会前的最后一个环节。 扪心自问，此时此刻的自己对于将来的生活工作仍然无法自知、缺乏信心。 所幸的是，在哥伦比亚大学，有Junfeng教授的指导，我将会拥有一个优越的环境。 我需要在这样一个环境里，去思考，去实践，去争取。

在这份学习计划中，我将总结自己对于未来的思考，整理出一份关于生活、学习和工作的计划。
\end{comment}

After 16 years of student life, I am going to finish my last phase of building and perfecting myself before taking a job and becoming an adult with duty. To be frank, right now I am still suffering a number of defects that slow me down from seeking the final target. Fortunately, it is so lucky of me to have the chance to continue my study advised by Professor Junfeng Yang at Columbia University, an excellent environment that allows me to think, to practise and to explore.

In this study plan, I am summarizing my thoughts of future and working on a detailed plan for live, study and work. It is about who I am, what I need, and how I can get it.

\input{SimpleSchedule.tex}

\input{targets.tex}

\input{methodology.tex}


%\newpage
%\baselineskip = 24pt
%\narrowtext
%\newpage
%\tableofcontents
%\newpage
%\listoffigures
%\newpage


\end{document}
