\section{What I need}

What am I living for? How can I feel no regret at the last moment of my life? 

\paragraph{Dear friends, relatives and girl friend} 
Human beings are not along. They live in the society. I do enjoy the time spent with my friends and relatives, by playing cards, having food, watching films and chatting. People live for themselves, but also for their friends and relatives. It is really hard to imagine that the boring life without friends, where one have no person to talk with, play with and share happiness and sorrow with.

In order to obtain sincere friends, I should never leave them behind when they are in trouble, keep them in mind in daily life, share my happiness and sorrow with them. Moreover, it only makes sense if I had the ability to handle their troubles and protect them from unhappiness.

On the other hand, it would always be critical in making friends. Not every cooperators are my friends. They are distinguished in purpose: cooperators' relation is based on profit, while friendship is not. The basic rule of making new friend should at least involve: similar interest, shared value, and selflessness.

Finding the other half of my life is also a serious business. Let me talk about it later.

\paragraph{Success and honor} 
They are the original desire for human beings. I used to reach a peak of my life in 2007, in which year I won the third place in International Olympiad in Informatics. In the following four years I spent a relatively plain time at Tsinghua University, but I also learnt a lot about myself and the life. I do, have a heart for competition and victory. I am also seeking for another peak in my life to prove myself to my wife, my parents, my teachers and my friends.

There are many kinds of success and honor, such as Bill Gates' wealth, Andrew Yao's Turing Award, Chairman Mao's political leadership, and Ming Yao's unbelievable social influence. However, I will win honors in my way. I am exploring techniques that improve people's life and win their respects. In contrast to \emph{DeMeter}, I prefer techniques like \emph{MoDist} and \emph{LOAN} since they have the ability to deal with practical issues. I am deeply influenced by the proud of IT "geeks", and I am not supposed to create a business in the way others do.

\paragraph{Significant contribution in certain area}
Winning a gold medal in IOI'07 makes nonsense to human beings centuries later, but I do wish to create something that \emph{improves millions of lives} and \emph{influences our descendants} even centuries later. My PhD direction lies in software reliability, security, distributed system and network. It is a fundamental research area, and somehow an auxiliary field for those business applications. But on the other hand, I can obtain a broad view of computer science community from my research. Then it is possible to extend my research to interesting and modern areas such like automation, cloud service, etc. I have the confidence to set up an attractive and promising research direction before the fourth year of the PhD program. At that time, opportunities and challenges will come.

\vspace{0.3in}

\paragraph{} Making targets into facts is always difficult. In August of 2011, I am leaving for US with a package of clothes, one thousand dollars and a personal laptop, and it is still a long journey to the goals of my life. In spite of those romantic targets, I have to set up practical ones before everything is too late.

\begin{itemize*} 
\item The most important, appropriate self-control and self-adjustment.
\item Build a healthy and strong body. It is the foundation of everything.
\item Proficient and solid technical skills.
\item Broad and in-depth understanding of my research area.
\item Earn enough money for personal purpose and emergent aid. 
\item Personal style and interests.
\end{itemize*}

